---
title: "Activity 2 - Simple Linear Regression"
author: "Saheli Sen"
date: "1/24/2023"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ****Day 1****

```{r}
library(tidyverse)
library(tidymodels)
library(ggplot2)
```

```{r}
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")
hfi
```

There are 123 variables and 1458 observations present.

```{r setup, include=FALSE}
hfi_2016 <- hfi %>% filter (year == 2016)
hfi_2016
hfi_2016 %>% select(pf_score, pf_expression_control)
```

## Simple Linear Regression

Below is a scatter plot of the two variables (note that the independent is on the horizontal axis and the dependent is on the vertical axis).

```{r Task3 Plotting relationship}

# Basic scatter plot with labels
sctrplt <- ggplot(hfi_2016, aes(x = pf_expression_control, 
                                y = pf_score)) + 
geom_point(size = 1, 
           color = "dodger blue")

sctrplt <- sctrplt + ggtitle("The relationship between Personal Freedom Score & Expression Control \n ") +
xlab("Personal Freedom Expression Control") + ylab("Personal Freedom Score")

# Change the color, size and face of the title, x and y axis labels

sctrplt <- sctrplt + 
theme(plot.title = element_text(color = "blue", 
                                size = 14,
                                face="bold.italic", 
                                hjust = 0.5),
axis.title.x = element_text(color="black", 
                            size=12, 
                            face="italic"),
axis.title.y = element_text(color="black", 
                            size=12, 
                            face="italic"))

sctrplt

```

As per the data appearance we can say that it follows a linear trend, and some R output for placing a linear model on this scatterplot, using regression analysis, is given below:

```{r Task4}

sctrplt <- sctrplt + 
geom_smooth(method = lm, 
            se = FALSE, 
            color = "black")

sctrplt
```

```{r Task5}
m1 <- lm(pf_score ~ pf_expression_control, data=hfi_2016)

#summary(m1)
tidy(m1)
```

